Transforming Trash as an Artistic Act

### 2015-12-29 chapter3_reduced.tex
Artworks
Former-commit-id: 1d407fb6662feff21c99012d4101d152fa73dcd2

How and why does trash draw attention of artists? In this chapter how artist approached to the trash and their techniques are discussed in the context of art. (Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?). How does it turn to medium?

%
%
\section{Root in the Art History}
Using trashed objects in making of art can be examined with the enterance of non-art objects to art\todo{sadece bu yeterli olmayabilir}. In other words, using objects in artworks beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together. (How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes. However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso. One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture. Using non-art objects in the production of art challenges existing conventions of painting. 
% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas. The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}

@@

\textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

@@

% TODO paraphrase
\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996 \cite{tauxe2012encyclopedia}.}

%
%
\summary{Collage}
Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}. \todo{read greenberg1984collage}

% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\summary{Hybridity} 
\paraphrase{Recycled object contains within it a reference to two or more distinct times. Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)} \todo{ref.}

% TODO MOVE
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{Different meanings for everybody.} 
%\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another. Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world. It is story of people --- the women, men, children etc. one person's trash into another's treasure.}

@@

%
%
\summary{Assemblage} 
Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}. \todo{Joseph Cornell, assemblage artist.}

%
%
\summary{Bricolage} 
Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time. \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}

%\begin{quote}
%[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project. His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
%\end{quote}

%[TODO use this ref]\cite{strasser1999waste}

@@

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors). From western trash to tribal treasure. \paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods. A disposable item becomes imminent desire and profound social consequence. (Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function. It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\todo{yerlinin fotoğrafı}
%\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head. In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}

@@

%Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p. 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p. 170). The finder discovers an unrealised significance in the object. A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object. He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context. \ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).

@@

% Amelie olabilir. Orada fotoğraf toplayan çocuk olabilir. Onları itinayla toplayan bir adam. Tren garındaki fotoğraf kulubesi. Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası. Bir birinden farklı bir sürü insan. Filmde neden böyle bir eyleme yer veriliyor? Film fotoğraflar üzerinden defter üzerinden ilerliyor. Onun çevresinden bir hikaye kurgulanıyor. İnsanların artıklarını topluyor. Onların değer vermedikleri şeyleri topluyor. Bunlar baya baya aslında o insanlar. Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor. Çok iyi bir örnek mi bilmiyorum. Burada niyet nedir ki? Ben buna şöyle bir okuma getireceğim diyebilirim. Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde. Bu arada bu fotoğraf toplama işi ilk değil. Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte. Ama benim işime yarayan kısmı ne? Neden o fotoğrafları ya da bunun filmini yapıyor. Aslında puzzlelar üretiyor. Belirli tekrar olacaktır. insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir. Tekrar bir kitap haline geliyor. Tanınmayan insanların fotoğrafları. Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon. Aslında tam da amelie bunu yapmıyor mu? Hikayeler üretiyor bu fotoğraflardan. Yeni karşılaşmalar üretmesi. Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır. Bin bir türlü şey vardır aralarında. Nereye yerleşmeli. Başkasının çöpünü toplama. O dönemin o eşyasını arşivini tutma. ve herkes sunuluyor sonrasında bu.

%
%
%[Ready-Mades]

%
%
\section{Examples from contemporary artists}
Beyond historical development of art with non-art objects and trash, for contemporary artist what it means has slight differences. Firstly their purpose do not want to express the language of art by using trash and non-art objects because they are already done and the way of making art dramatically changed. Therefore what are their purpose and how they can be viewed?

% not easily understandable with the entering non-art objects in art. artist are responding the current societies habits in a different ways. what they are doing here is to see other possibilities and show actually what is going on. what does it mean all of these things.

% FROM ReVista
%\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} 
\paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

% FROM Paola Ibarra ReVista
\paraphrase{Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere. Is there a limit to recycling and representation? Or is there a point at which waste cannot become art (or anything else)?}

% TODO Naive debate??
\comment{All that can be seen as naive act because of little impact and outside of the system(which system?). As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill. However this very argumentative that having no impact or little impact. It might be true that this practices solve all problems of landfill or etc. But changes individuals and communities life. It recreate and rebuilds the community. Even if it is one simple object worth look and see the opportunities of it.}

%
% Tags: "dikkate alınmayanı tekrar ele alıyor". Mekan: sokaklar, şehir, kamusal alan. Traces of our life.
\textbf{Road Kill.} \paraphrase{Filomena Cruz creates photographic series named as \quotes{Road Kill} painstakingly captures tiny \quotes{trash corpses} on the pavement. It is that particular type of trash meet in the public places. Trash left behind, trash on the sidewalk, squished, squashed, and weathered. Filomena Cruz sees trash that people don’t want to see. A piece of chewing gum with an \quotes{engraved} leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of \quotes{worthlessness} suddenly becoming meaningful (and moving). For one thing, trash corpses faithfully record city life.} Uses public spaces and takes photos of streets and roads in unfamiliar fashion, focussing onto trash. Captures the trace of city life from trash. She does not collect the trash physically, collects the images of them. They are still there and continously changing.

@@

%
%
%\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.

%
%
\textbf{Pictures of Garbage.} Vic Muniz creates monumental portraits from trash in Jardim Gramacho, an open-air dump just outside Rio, with the help of \textit{catadores} in the documentary film (Waste Land, 2010) Waste Land, directed by Lucy Walker. Called “Pictures of Garbage,” they were created by Mr. Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America. (Important point is here collaboration with the pickers. Listening their stories and capturing their portraits. It methods similar to the mosaics, every type of discard collected from dump used his photos.) Trash and people who live there is the subject of his portraits. None of the trash is belong to that people. However again these trash express them perfectly because they make a life from trash. Their home is dump.

@@

%
%
\textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their \quotes{Recycled Orchestra}.

Cateura, Paraguay is a small city that has grown atop a massive dump. It is regarded as one of the poorest slums in Latin America, a village where people live among a sea of garbage. Incredibly, the landfill itself is the primary form of subsistence for many residents, who pick through waste for items that can be used or sold. Prospects for most of the children born in Cateura is bleak as gangs and drugs await many of them. But then one day, something amazing happened. A garbage picker named Nicolás Gómez (known as “Cola”) found a piece of trash that resembled a violin and brought it to musician Favio Chávez. Using other objects collected from the dump, the pair constructed a functional violin in a place where a real violin is worth more a house. Using items gleaned completely from the dump, the pair then built a cello, a flute, a drum, and suddenly had a wild idea: could a children’s orchestra be born in one of the most depressed areas in the world? As you can guess, the answer was yes.

>>>>

In this chapter, questioned the purpose and meaning of using trash as a medium in the artworks. The reasons and motivations of artists who use trash are analyzed. The artist uses discarded items in their work is analyzed in the light of arguments discussed in the previous chapter. Questioned that why artists select to use society's debris rather than fresh items. Researched the place of trash in the world of art by looking at different methods and approaches. Started from masterpieces and founding works. Continued with recent examples of artworks.

% Çöpün sanatta kullanılmasının temelleri arastirilmakta.

Firstly looked at how artist started using objects that are not produced by artist and with the purpose of making art. Their works are notable and founding works that open new dimensions to reconsider objects and their meaning. Further, they extended the ways of art making and the language of art. Therefore, it is important to analyze Their intent and methods are analyzed (how?). In other words, looked at the foundation of using non-art objects in the art making. First examples are analyzed and how it evolved over time is explored. Questioned that how they affected successor artist.

Secondly looked at the some examples of contemporary works (or works from recent history). In particular, capture the current approaches on trash. Several methods and genres are explored.

Lastly focused on the inspiring documentary of Agnes Varda, The Gleaners and I which provides a general picture of the subject.

%
%
\section{Root in the Art History}
Using trashed objects in making art can be examined with the entrance of non-art objects into the art. In other words, using objects in different scope beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting (or juxtaposing) them together. (How using non-art objects affected art? Fragments) Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes. However, it is not discussed in the context of fine art and not accepted method for art making.

From the beginning of 20th-century non-art, objects draw the attention of the artist. Development of art in this century evolved through this non-art objects (or these objects play significant role development of art trough time). They bring new dimension (or perception) to consider objects. Usage of these objects dramatically changed the way people look at art. In short, they introduced a new way of making art.

One of the remarkable change in the 20th-century art is the using unconventional materials in the making of paintings and sculptures, rather than the original (pure, fresh) materials produced with the purpose of art. These objects are not normally considered as art, often because they already have a non-art function. Possibly they are part of different disciplines and markets. Their place in the society and people's mind commonly have a different meaning. Beyond them, artists started to use them for their own purposes. Objects gain different meanings and usages with the hands of artists. (It is explained in the previous chapter that objects are not static and absolute. Objects can be used for new purposes even if they lost their meaning and value in the conventional system.)

They questioned the way of traditional (conventional) way of art making in every dimension. Their approach out of the previous methods. They are looking for the beyond of painting. With using different objects they break the pureness of artwork. It is not pure anymore, fragmented. Boundaries are pushed. Using non-art objects in the production of art challenges existing conventions of painting.

Using non-art object can be considered as moving away from the purification of art \todo{ref req}. It is a composition of different fragments and pieces. Rather than the traditional way of painting on canvas they composed their work with the combination of various objects from different context. With this approach works can be examined in multi-dimensional context.

% (Peki neden sanatçılar bunu tercih ettiler, buhran neydi? Azıcık öncesindeki kıpırdanmaları anlatmak gerekli. Bu apayrı ve uzun bir konu. Ama değişmeler yavaş yavaş gelmeye başlamıştı. Neye karşıydı, ne getirdi. Sanatın var olan kalıplarını yıkıp yerine ne koydu? ronesanstan beri gercekligin temsili uzerine kurulan sanat ve estetik anlayis coktan sorgulanmaya baslamistir izlenimcilerle birlikte.)

Before the 20th-century, artists started to inquiry the existing methods and themes of previous periods. Modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art. Previously paintings are based on linear perspective and realistic style. Themes are often composed of religious and mythical narratives \todo{MOMA ref}. After the second half of the 19th-century, they started to abandon these themes and painting methods. For instance, in the works of impressionist paint brushstrokes can be easily identified, and themes are composed of everyday scenes. With Cezanne, the linear perspective started to question and later reached to its peak point with cubism. Cubism is developed with the collaboration of the Picasso and Braque. Besides, these two artists experimented non-traditional materials in their works for the first time in the scope of fine art. They continuously produced works with using different objects. They support each others art. They showed that an endless potential lay there. They collaborated with each other on the development of cubism and collage.

One of the keys to understanding the importance of Cubism, of Picasso and Braque, is to consider their actions and how unusual they were for the time. When Braque, and then Picasso placed industrially-produced objects ("low" commercial culture) into the realm of fine art ("high" culture) they acted as artistic iconoclasts (icon=image/clast=destroyer). \todo{ref}

% Sanat disi objenin kullanilmasi aslinda sanatin saflasmasininda disinda yer almaktadir. Saf oz bir sekilde kurulmasindan ziyade farkli seylerin parcalarin bir araya gelmesiyle birlikte kullanilmasi. Tabuların yıkılması. Sınırlarının aşılması. geleneksel anlamda tuvalin uzerine boya surmekten ziyade farkli teknikler denenmeye baslanmistir. 20yuzyilda geleneksel sanat tum boyutlariyla yeniden ele alinmistir. Resmin konusu, sergileme bicimleri, yenikikler gostermistir.

Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.

Collage was a major turning point in the evolution of Cubism, and therefore a major turning point in the whole evolution of modernist art in this century \cite{greenberg1984collage}.

Similar to the collage, assamblage is produced by the incorporation of three-dimensional elements. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials. \todo{ref.}

%Who invented collage--Braque or Picasso--and when is still not settled. because of most of their early works are undated and unsigned. the question of priority is less important rather than

One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture. Picasso combined painting with already existing materials. He used real objects to represent instead of painting. As mentioned in the name of the work Picasso give clues of the parts of it. For instance the oval canvas\todo{canvas or oilcloth?} and the rope around it represent the table. Pasted chair caning signifies the chair within the table. On the table folded paper shadow represent newspaper. Further there is a cut out lemon painted onto the table. \paraphrase{The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness. This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.}

% Greenberg
% The abiding effect is of a constant shuttling between surface and depth, in which the depicted flatness is "infected" by the undepicted. Rather than being deceived, the eye is puzzled; instead of seeing objects in space, it sees nothing more than--a picture.

% \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}

@@

Moreover, they questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the rarefied, contemplative realm of artistic creation. Of equal importance, their work highlighted and separated the role of technical skill from art-making. Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of high and low, of unique and mass-produced objects. They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"

% http://www.nybooks.com/articles/2010/12/09/artist-everything/
% http://www.artchive.com/artchive/S/schwitters.html
After Picasso and Baraque, many artists applied collage and assamblage techniques to their works. Dada artist Kurt Schwitters is one of the productive artists of them. In 1918 created his own form of Dada in Hanover called 'Merz', using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions. The nonsense word 'Merz' is generated from the name of the name of a bank: the Kommerz und Privatbank. Merz was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt Merz Schwitters or simply Merz.

"The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way. In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism." (Gwendolyn Webster)\todo{ref}

% http://www.artchive.com/artchive/S/schwitters.html
Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.\todo{ref}

Merzbau is most important ones. In 1937 after his work had been included in the Degenerate Art Exhibition he fled Germany for Norway. There he created a second Merzbau. In 1940 he found refuge in England where he started a third Merzbau at Ambleside in the Lake District. The first Merzbau was destroyed in the Second World War, the second by fire in 1951 and the third was left unfinished at his death in 1947. It is now preserved in the Hatton Gallery of the University of Newcastle upon Tyne.

% Yaptığı işte ısrarcı ve üretken. Sürekli inşa ettiği yapılar merzbaular aslında bitmiş bir izlenimi vermiyor. sürekli büyüyor değişiyor. sabit ve bitmiş bir yapısı bulunmamakta.

Recycled object contains within it a reference to two or more distinct times. Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them". \todo{ref}

Collages and assemblages can be composed of all types of objects such as trash and found object. The notion of found object is researched by the many scholars \todo{ref.}, but usage in the art has gained new dimensions with the Duchamp's concept of readymade. Industrially manufactured or anything found  anymore can found a place in the art. The most famous example is Fountain (1917) (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side. Before that first one is Bicycle Wheel. He mounted the bicycle wheel upside down onto a stool. 
% http://www.moma.org/learn/moma_learning/marcel-duchamp-bicycle-wheel-new-york-1951-third-version-after-lost-original-of-1913
When Bicycle Wheel was first displayed, Duchamp encouraged viewers to spin the wheel. (Participation of the audience) Although he claimed to select objects for his readymades without regard to beauty, he said, “To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.”

@@

% TODO Bunu sadece referans olarak kullanabilirsin, çünkü zaten çok fazla tekrar var.
%\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996 \cite{tauxe2012encyclopedia}.}

% TODO rubbish theoryinin başına konulabilir, referans olarak kullanılabilir.
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{Different meanings for everybody.} 
%\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another. Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world. It is story of people --- the women, men, children etc. one person's trash into another's treasure.}

@@

@@

% TODO will not be used. just for rerefence
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors). From western trash to tribal treasure. \paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods. A disposable item becomes imminent desire and profound social consequence. (Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}

% TODO will not be used. just for reference
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function. It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.

% TODO will not be used. just for reference
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\todo{yerlinin fotoğrafı}
%\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head. In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}

@@

\paraphrase{Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p. 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p. 170). The finder discovers an unrealised significance in the object. A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object. He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context. \ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).} \todo{parap. ref.}

\paraphrase{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998). Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}

@@

%
%
\section{Examples from contemporary artists}
In the light of discussions at previous section, some of the works (or current strategies and approaches ) of artist are analyzed. First one is related with found objects.

% Neden bu işler, neden bu sıra?

% Neden çöpü kullanıyorlar. Bunu belirmek gerekli. İlki sanata farklı bir obje sokarak saflığını bozma, hazır yapım ile geleneksel yöntemlere karşı çıkış, fikrin ön plana çıkması. Visual uniqueness, aesthetics dimension, Economic reasons

Photobooths are machines that place crowded places and with affordable cost people can get their photos. It is a pheonema that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as a two volume.

In the French film Amélie\footnote{Original title: Le fabuleux destin d'Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris. He collects them and glue them together in a photo album. In the film photo booths and found photos are central catalytic. Amélie falls in love with him when she realize him searching for found photos. After his photo album passed to Amélie, she looks every page of photo album again and again. Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away. The important part of the film it generates images of a man who scanvage the photos of another people. There are a lot of artist who collects discarded items but their process is not well documented. Therefore we are not aware of the artist process.

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
  \caption{Still image from Amélie}
  \label{fig:Amelie}
\end{figure}

Prior to film Amélie, British artist Dick Jewell published a book in title of "Found Photos" in 1977. It is a collection of photobooth images that had been thrown away or torn up by the people in the photos. Ian Walker comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine. They are scavenged by the artist from the photo booths of London. The reasons of why photos are rejected vary including technical problems like flash or posing time. On the other hand, some of them are very good condition, and it is a mystery that why they are rejected. Walker explains that the \todo{block qoute} "gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving." Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them. "Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ‘readymades’." His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin. Badger describes Found Photos as ‘both a conceptual artwork and a sociological footnote’.

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

On the other side for another artist photographs serve a function to record his daily trash. Tim Gaudreau photographed every object that he threw away for one year. At the end around five thousand images are covered all the gallery and opened to visitors. He notes that it just started as a documentation of his discards, but later it became (part of his life and) an obsession that he can not able to easily quit off. He says that "this collection of images intimately displays what I do, what I consume. It reveals me." Like in the case of Tracey Emin trash turns to a medium that is used to express oneself. People are not only composed of the listed items in the CVs like in the film Fight Club Tyler Durden draws attention to the narrator by saying: "You are not your bank account". It is an effective way of looking things left behind rather that things put forward. Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.

Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement. In her photographic series "Road Kill", she captures tiny "trash corpses" that are generally ignored and out of sight. In other words, the skin of city revealed through her photos in micro scale. On the skin of city there are lots of trash including "a piece of chewing gum with an "engraved" leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful" as looked through the window of they capture the city life and skin of the city that we touched. She shows us tiny details of huge cities. (Somehow these trashes for all effort succeeded to stay in the towns.) These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.

@@

In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump. He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millons of people. Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump. He selects unusual materials and people for potraits rather than the powerful and notable people as commonly encountered at Renaissance. To create portraits of \textit{catadores} there is any other material than trash because of they are already build up their life in trash of city. [Also these image are sold an auction and earned money donated to the \textit{catadores}. The images of trash moved to beloved places such as homes and museums. As stated in the rubbish theory they transformed to a durable object.]

@@

Not only monumental portraits extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez. Favio Chávez is a music teacher, and Nicolás Gómez is a garbage picker. They live in Cateura at Paraguay. It is a one of the poorest villages where people live among the sea of garbage. "A violin is worth more than a house here," says Favio Chavez in documentary film. The orchestra's director and founder. Favio Chavez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez. Players of the orchestra are compiled from the children who are hopeless for their future. In the midst of such an existence, these musicians have created something both special and truly awe-inspiring. They are given birth to an orchestra that plays the masterpieces of classical music composed by Mozart, Beethoven, and Vivaldi. Trash turned to treasure and totally ironic that a signifiers of high culture like classical music can be even played with imperfect instruments. For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music. (To enjoy and play such music requires economic wealth and it is not possible for everyone.) What they create is actually not expected from them, and their success is not limited with their location. They have given concerts around the world.

%"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either." \quotes{The world send us garbage. We send back music}.

% Resistance to all hard conditions
